---
title: "Cities prelim analysis"
author: "Jeff Witmer"
date: "11/1/2020"
output:
  html_document:
    fig_height: 4
    fig_width: 6
  html_notebook: default
  word_document:
    fig_height: 4
    fig_width: 6
  pdf_document:
    fig_height: 5
    fig_width: 7
---

We now have data entered for 32 cities on each of several variables. This now includes police demographics.


```{r setup, message=FALSE,  warning=FALSE}
## Libraries to include
library(tidyverse)
library(mosaic)
## Load the data
library(readxl)
#NewCities <- read_excel("New Cities Database copy late reduced 10-27-20.xlsx")
#NewCities <- read_excel("New Cities Database copy 10-28-20.xlsx")
NewCities <- read_excel("New Cities Database copy noNAs 11-1-20.xlsx")
```

Look at the structure of the datafile.
```{r}
str(NewCities)
```


The primary variables are DiffBlackMinusWhite, RatioBlackWhite, animus_score, and implicit_score_mean. 
```{r}
Cities <- NewCities %>% select(c(City, year, DiffBlackMinusWhite, RatioBlackWhite, animus_score, implicit_score_mean, Region))
dim(Cities)
```

```{r}
head(Cities)
```


A scatterplot matrix.
```{r}
plot(Cities[2:6])
```

There are a few high points for RatioBlackWhite. They are for California:
```{r}
Cities[order(Cities$RatioBlackWhite, decreasing = TRUE),]
```

 It will be helpful to have R know that Region is a factor.
```{r}
NewCities$Region <- as.factor(NewCities$Region)
str(NewCities)
```


Let's look at RatioBlackWhite as a response to a couple of predictors. It seems that I need to use as.factor() despite resetting Region as a factor above.
```{r}
plot(RatioBlackWhite ~ animus_score, col = as.factor(Region), data = Cities)
plot(RatioBlackWhite ~ animus_score, data = Cities)
plot(RatioBlackWhite ~ implicit_score_mean, col = as.factor(Region), data = Cities)
plot(RatioBlackWhite ~ year, col = as.factor(Region), data = Cities)
plot(animus_score ~ implicit_score_mean, col = as.factor(Region), data = Cities)
```

The mPlot() command is useful for exploring the data. After using it, I came up with this plot, for example:
```{r}
gf_point(implicit_score_mean ~ RatioBlackWhite, data = Cities, color = ~ Region) %>% 
gf_theme(legend.position = "right") %>% 
gf_labs(title = "", caption = "")
```

Here is a plot that shows (in log scale) that when WhitePoliceShare is below 60% RatioBlackWhite is high. (Recall that RatioBlackWhite is the relative probability of a Black driver being stopped to that of a White driver being stopped, and is our main response variable of interest.)
```{r}
gf_point(RatioBlackWhite ~ WhitePoliceShare, data = NewCities, color = ~ implicit_score_mean) %>%
gf_smooth() %>%
gf_refine(scale_y_log10()) %>% 
gf_theme(legend.position = "top") %>% 
gf_labs(title = "", caption = "")
```


Another graph, not about stops but about implicit mean score and police force demographics.
```{r}
gf_point(WhitePoliceShare ~ implicit_score_mean, data = NewCities, color = ~ animus_score) %>%
gf_lm() %>% 
gf_theme(legend.position = "top") %>% 
gf_labs(title = "", caption = "")
```

A similar graph, not about stops but about animus score and police force demographics.
```{r}
gf_point(WhitePoliceShare ~ animus_score, data = NewCities, color = ~ implicit_score_mean) %>%
gf_lm() %>% 
gf_theme(legend.position = "top") %>% 
gf_labs(title = "", caption = "")
```



```{r}
summary(mod1 <- lm(RatioBlackWhite ~ animus_score + implicit_score_mean, data = Cities))
summary(mod2 <- lm(RatioBlackWhite ~ implicit_score_mean, data = Cities))
```

Consider Year also.
```{r}
summary(mod1yr <- lm(RatioBlackWhite ~ animus_score + implicit_score_mean + year, data = Cities))
summary(mod2yr <- lm(RatioBlackWhite ~ implicit_score_mean + year, data = Cities))
summary(modyYearOnly <- lm(RatioBlackWhite ~ year, data = Cities))
```
