---
title: "Cities prelim analysis"
author: "Jeff Witmer"
date: "10/28/2020"
output:
  html_document:
    fig_height: 4
    fig_width: 6
  html_notebook: default
  word_document:
    fig_height: 4
    fig_width: 6
  pdf_document:
    fig_height: 5
    fig_width: 7
---

We now have data entered for 32 cities on each of several variables. I want to start playing with the data.


```{r setup, message=FALSE,  warning=FALSE}
## Libraries to include
library(tidyverse)
## Load the data
library(readxl)
NewCities <- read_excel("New Cities Database copy late reduced 10-27-20.xlsx")

```

Look at the structure of the datafile.
```{r}
str(NewCities)
```

For some reason some of the variables are chr, but they should be num.
```{r}
#NewCities$RatioBlackWhite <- as.numeric(as.character(NewCities$RatioBlackWhite))
NewCities$DiffBlackMinusWhite <- as.numeric(NewCities$DiffBlackMinusWhite)
NewCities$RatioBlackWhite <- as.numeric(NewCities$RatioBlackWhite)
NewCities$implicit_score_mean <- as.numeric(NewCities$implicit_score_mean)
str(NewCities)
```



The primary variables are DiffBlackMinusWhite, RatioBlackWhite, animus_score, and implicit_score_mean. 
```{r}
Cities <- NewCities %>% select(c(City, year, DiffBlackMinusWhite, RatioBlackWhite, animus_score, implicit_score_mean))
dim(Cities)
```

```{r}
head(Cities)
```


A scatterplot matrix.
```{r}
plot(Cities[2:6])
```

There are a few extreme points for RatioBlackWhite. They are for Oakland:
```{r}
Cities[order(Cities$RatioBlackWhite, decreasing = TRUE),]
```

Let's look at RatioBlackWhite as a response to a couple of predictors.
```{r}
plot(RatioBlackWhite ~ animus_score, data = Cities)
plot(RatioBlackWhite ~ implicit_score_mean, data = Cities)
plot(RatioBlackWhite ~ year, data = Cities)
#plot(animus_score ~ implicit_score_mean, data = Cities)
```

```{r}
summary(mod1 <- lm(RatioBlackWhite ~ animus_score + implicit_score_mean, data = Cities))
summary(mod2 <- lm(RatioBlackWhite ~ implicit_score_mean, data = Cities))
```

Consider Year also.
```{r}
summary(mod1yr <- lm(RatioBlackWhite ~ animus_score + implicit_score_mean + year, data = Cities))
summary(mod2yr <- lm(RatioBlackWhite ~ implicit_score_mean + year, data = Cities))
summary(modyYearOnly <- lm(RatioBlackWhite ~ year, data = Cities))
```
