---
title: "Analysis using NewerCities data"
author: "Jeff Witmer"
date: "11/10/2020"
output:
  html_document:
    fig_height: 4
    fig_width: 6
  html_notebook: default
  word_document:
    fig_height: 4
    fig_width: 6
  pdf_document:
    fig_height: 5
    fig_width: 7
---

We have data entered for 31 cities (we are leaving out Idaho Falls) on each of several variables. The file NewerCitiesDatabase contains all of the variables.

```{r setup, message=FALSE,  warning=FALSE}
## Libraries to include
library(tidyverse)
library(mosaic)
## Load the data
NewCities <- read.csv("~/JuniorPracticumGitHub/NewerCitiesDatabase.csv")
```

Look at the structure of the datafile.
```{r}
str(NewCities)
```

The mplot() command is useful; but first I should define some city demographic variables. 
And maybe I should filter on year, so that each city shows up only once, in a preliminary analysis.
How should we measure whiteness of a police force relative to a city?
```{r}
NewCities <- NewCities %>% mutate(WhPoliceExcess = WhitePoliceShare/WhitePopShare)
Only2015 <- NewCities %>% filter(year == 2015)
```


Look for  high points for WhPoliceExcess 
```{r}
Only2015[order(Only2015$WhPoliceExcess, decreasing = TRUE),]
```


From mplot() I got this graph, showing that when the Black population share is low, the ratio of Black to White probability of being stopped is high.
```{r}
gf_point(RatioBlackWhite ~ BlackPopShare, data = NewCities) %>%
gf_smooth() %>%
gf_refine(scale_y_log10()) %>% 
gf_labs(title = "", caption = "")
```


